Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
beginning of genealogy section

@@

>>>>

\begin{center}
{\footnotesize
\begin{tikzpicture}[>=stealth',semithick]

\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (cantor) { Cantor };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=cantor, node distance=3cm] (additions) { Additions };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=3cm] (additions) { Goedel };

\end{tikzpicture}
}
\end{center}

@@

\section{Comparison of \Hydras with other Coq books}
